### 2014-06-20 reports/report.Rmd
report tables improved

```{r echo=FALSE, comment=''}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%.dat$dictionary$Variable[.dat$dictionary$Group=="tree"]]
cbind(counts)
```

@@

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
options(width =160)
locLevelInfo(.dat$data)
```

>>>>

```{r echo=FALSE, comment='',results='asis'}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%.dat$dictionary$Variable[.dat$dictionary$Group=="tree"]]
kable(cbind(counts))
```

@@

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results='asis'}
options(width =160)
kable(locLevelInfo(.dat$data))
```
